Model LF

### 2022-10-18 max_dp endogen stød.Rmd

```{r}
###Gengivelse af stød til model
max_dp_sbs2_low = sens_2_bs_low$simulation$max_dp
wage_sbs2_low = sens_2_bs_low$simulation$wage
komp_r_sbs2_low = sens_2_bs_low$simulation$komp_r
part_sbs2_low = sens_2_bs_low$simulation$part
yk_ds_sbs2_low = sens_2_bs_low$simulation$yk_ds
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
wage_ds_t_sbs2_low = sens_2_bs_low$simulation$wage_ds_t
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
max_gap_sbs2_low = sens_2_bs_low$simulation$max_gap
wage_gap1_sbs2_low = sens_2_bs_low$simulation$wage_gap1
inflation_sbs2_low = sens_2_bs_low$simulation$inflation
wage_ds_sbs2_low = sens_2_bs_low$simulation$wage_ds
emp_sbs2_low = sens_2_bs_low$simulation$emp
nl_g_sbs2_low = sens_2_bs_low$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_low = sens_2_S1_low$simulation$max_dp
wage_s2_low = sens_2_S1_low$simulation$wage
komp_r_s2_low = sens_2_S1_low$simulation$komp_r
emp_s2_low = sens_2_S1_low$simulation$emp
yk_ds_s2_low = sens_2_S1_low$simulation$yk_ds
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
wage_ds_t_s2_low = sens_2_S1_low$simulation$wage_ds_t
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
max_gap_s2_low = sens_2_S1_low$simulation$max_gap
wage_ds_s2_low = sens_2_S1_low$simulation$wage_ds
wage_gap1_s2_low = sens_2_S1_low$simulation$wage_gap1
wage_gap_s2_low = sens_2_S1_low$simulation$wage_gap
nl_g_s2_low = sens_2_S1_low$simulation$nl_g
inflation_s2_low = sens_2_S1_low$simulation$inflation
```

@@

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs2_up = sens_2_bs_up$simulation$max_dp
wage_sbs2_up = sens_2_bs_up$simulation$wage
komp_r_sbs2_up = sens_2_bs_up$simulation$komp_r
part_sbs2_up = sens_2_bs_up$simulation$part
yk_ds_sbs2_up = sens_2_bs_up$simulation$yk_ds
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
wage_ds_t_sbs2_up = sens_2_bs_up$simulation$wage_ds_t
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
max_gap_sbs2_up = sens_2_bs_up$simulation$max_gap
wage_gap1_sbs2_up = sens_2_bs_up$simulation$wage_gap1
inflation_sbs2_up = sens_2_bs_up$simulation$inflation
wage_ds_sbs2_up = sens_2_bs_up$simulation$wage_ds
emp_sbs2_up = sens_2_bs_up$simulation$emp
u_ds_sbs2_up = sens_2_bs_up$simulation$u_ds
nl_g_sbs2_up = sens_2_bs_up$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_up = sens_2_S1_up$simulation$max_dp
wage_s2_up = sens_2_S1_up$simulation$wage
komp_r_s2_up = sens_2_S1_up$simulation$komp_r
emp_s2_up = sens_2_S1_up$simulation$emp
yk_ds_s2_up = sens_2_S1_up$simulation$yk_ds
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
wage_ds_t_s2_up = sens_2_S1_up$simulation$wage_ds_t
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
max_gap_s2_up = sens_2_S1_up$simulation$max_gap
wage_ds_s2_up = sens_2_S1_up$simulation$wage_ds
wage_gap1_s2_up = sens_2_S1_up$simulation$wage_gap1
wage_gap_s2_up = sens_2_S1_up$simulation$wage_gap
u_ds_s2_up = sens_2_S1_up$simulation$u_ds
inflation_s2_up = sens_2_S1_up$simulation$inflation
nl_g_s2_up = sens_2_S1_up$simulation$nl_g
```

@@

@@

```{r}
plot((emp_s2_up-emp_sbs2_up)*1000, col= "red")
```

@@

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(0.9, 1.1), main= "Productivity");
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.2"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
plot((nl_g_s3_low-nl_g_sbs3_low), col= "red")
```

>>>>

```{r}
###Gengivelse af stød til model
max_dp_sbs2_low = sens_2_bs_low$simulation$max_dp
wage_sbs2_low = sens_2_bs_low$simulation$wage
komp_r_sbs2_low = sens_2_bs_low$simulation$komp_r
part_sbs2_low = sens_2_bs_low$simulation$part
yk_ds_sbs2_low = sens_2_bs_low$simulation$yk_ds
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
wage_ds_t_sbs2_low = sens_2_bs_low$simulation$wage_ds_t
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
max_gap_sbs2_low = sens_2_bs_low$simulation$max_gap
wage_gap1_sbs2_low = sens_2_bs_low$simulation$wage_gap1
inflation_sbs2_low = sens_2_bs_low$simulation$inflation
wage_ds_sbs2_low = sens_2_bs_low$simulation$wage_ds
emp_sbs2_low = sens_2_bs_low$simulation$emp
nl_g_sbs2_low = sens_2_bs_low$simulation$nl_g

emp_sbs2_low = sens_2_bs_low$simulation$emp
ik_sbs2_low = sens_2_bs_low$simulation$ik
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_low = sens_2_S1_low$simulation$max_dp
wage_s2_low = sens_2_S1_low$simulation$wage
komp_r_s2_low = sens_2_S1_low$simulation$komp_r
emp_s2_low = sens_2_S1_low$simulation$emp
yk_ds_s2_low = sens_2_S1_low$simulation$yk_ds
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
wage_ds_t_s2_low = sens_2_S1_low$simulation$wage_ds_t
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
max_gap_s2_low = sens_2_S1_low$simulation$max_gap
wage_ds_s2_low = sens_2_S1_low$simulation$wage_ds
wage_gap1_s2_low = sens_2_S1_low$simulation$wage_gap1
wage_gap_s2_low = sens_2_S1_low$simulation$wage_gap
nl_g_s2_low = sens_2_S1_low$simulation$nl_g
inflation_s2_low = sens_2_S1_low$simulation$inflation

ik_s2_low = sens_2_S1_low$simulation$ik
```

@@

```{r}
plot(wage_gap1_s2_low, col= "red", main= "Wage-gap (38%) inclusive inflation", ylab= "Wage-gap in % of wage" );grid()
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs2_up = sens_2_bs_up$simulation$max_dp
wage_sbs2_up = sens_2_bs_up$simulation$wage
komp_r_sbs2_up = sens_2_bs_up$simulation$komp_r
part_sbs2_up = sens_2_bs_up$simulation$part
yk_ds_sbs2_up = sens_2_bs_up$simulation$yk_ds
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
wage_ds_t_sbs2_up = sens_2_bs_up$simulation$wage_ds_t
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
max_gap_sbs2_up = sens_2_bs_up$simulation$max_gap
wage_gap1_sbs2_up = sens_2_bs_up$simulation$wage_gap1
inflation_sbs2_up = sens_2_bs_up$simulation$inflation
wage_ds_sbs2_up = sens_2_bs_up$simulation$wage_ds
emp_sbs2_up = sens_2_bs_up$simulation$emp
u_ds_sbs2_up = sens_2_bs_up$simulation$u_ds
nl_g_sbs2_up = sens_2_bs_up$simulation$nl_g
ik_sbs2_up = sens_2_bs_up$simulation$ik
pconk_ds_sbs2_up = sens_2_bs_up$simulation$pconk_ds

xk_ds_sbs2_up = sens_2_bs_up$simulation$xk_ds
mk_ds_sbs2_up = sens_2_bs_up$simulation$mk_ds
net_balance_sbs2_up= xk_ds_sbs2_up - mk_ds_sbs2_up
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_up = sens_2_S1_up$simulation$max_dp
wage_s2_up = sens_2_S1_up$simulation$wage
komp_r_s2_up = sens_2_S1_up$simulation$komp_r
emp_s2_up = sens_2_S1_up$simulation$emp
yk_ds_s2_up = sens_2_S1_up$simulation$yk_ds
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
wage_ds_t_s2_up = sens_2_S1_up$simulation$wage_ds_t
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
max_gap_s2_up = sens_2_S1_up$simulation$max_gap
wage_ds_s2_up = sens_2_S1_up$simulation$wage_ds
wage_gap1_s2_up = sens_2_S1_up$simulation$wage_gap1
wage_gap_s2_up = sens_2_S1_up$simulation$wage_gap
u_ds_s2_up = sens_2_S1_up$simulation$u_ds
inflation_s2_up = sens_2_S1_up$simulation$inflation
nl_g_s2_up = sens_2_S1_up$simulation$nl_g

ik_s2_up = sens_2_S1_up$simulation$ik
pconk_ds_s2_up = sens_2_S1_up$simulation$pconk_ds

xk_ds_s2_up = sens_2_S1_up$simulation$xk_ds
mk_ds_s2_up = sens_2_S1_up$simulation$mk_ds
net_balance_s2_up= xk_ds_s2_up - mk_ds_s2_up

@@

```{r}
plot((ik_s2_up/ik_sbs2_up), col= "red", main= "% Change in Investments");
lines((ik_02/ik_00), col="black");
legend("left", legend=c("Wage Gap limit 42%",
                       "Wage gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((pconk_ds_s2_up/pconk_ds_sbs2_up), col= "red", main= "% change in Consumption");
lines((pconk_ds_02/pconk_ds_00), col="black");
legend("left", legend=c("Wage Gap limit 42%",
                       "Wage gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((net_balance_s2_up/net_balance_sbs2_up), col= "red", main= "% Change in net Trade balance");
lines((net_balance_02/net_balance_00), col="black");
legend("left", legend=c("Wage Gap limit 42%",
                       "Wage gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((yk_ds_s2_up/yk_ds_sbs2_up), col= "red", main= "% Change in GDP");
lines((yk_ds_02/yk_ds_00), col="black");
legend("left", legend=c("Wage Gap limit 42%",
                       "Wage gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
plot((emp_s2_up-emp_sbs2_up)*1000, col= "red", main= "Change in employed (people)");grid()
```

@@

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(0.9, 1.1), main= "% Change in Productivity");
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.26"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((yk_ds_s3_low/yk_ds_sbs3_low), col= "red", ylim= c(min(yk_ds_s3_low/yk_ds_sbs3_low), max(yk_ds_03/yk_ds_bs3)), main= "% Change in GDP");
lines((yk_ds_03/yk_ds_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.26"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
plot((nl_g_s3_low-nl_g_sbs3_low), col= "red", ylab= "Change in Gov (people)", main= "Government net-lednings estimate set to 0.1"); grid()
```
